# My First knitr Document
Jeremiah Tantongco

## Introduction

```{r setoptions, echo=FALSE}
#Makes it so that executed code will by default not be displayed
library(knitr)
opts_chunk$set(echo=F, results='hide')

#asis -> no R pre/post html processing
#hide -> do not display
#fig.height: numeric
#fid.width: numeric
#cache = true -> to save results, update requires recaching
# caching not usable in cases where there are code side effects
```

This is some text (ie a "text chunk"). Here is a code chunk but it doesn't print anything!

echo option is whether you want to print code out in document
results is the command line output of the code

```{r simulation, echo=FALSE,results='hide'}
#```{r simulation, echo=FALSE} 
set.seed(1)
x <- rnorm(100)
mean(x)
```

```{r computetime,echo=FALSE}
time <- format(Sys.time(),"%a %b %d %X %Y")
rand <- rnorm(1)
```

The current time is `r time`. My favorite random number is `r rand`.

Let's first simulate some data
```{r simulatedata, echo=TRUE}
x <- rnorm(100); y <- x + rnorm(100, sd=0.5)
```

Here is a scatterplot of the data

```{r scatterplot, fig.height=4}
#note embeds the image in the html file and not separate img file
par(mar=c(5,4,1,1), las=1)
plot(x,y, main = "My Simulated Data")
```

```{r fitmodel}
library(datasets)
data(airquality)
fit <- lm(Ozone ~ Wind + Temp + Solar.R, data=airquality)
```

Here is a table of regression coefficients
```{r showtable, results='asis'}
library(xtable)
xt <- xtable(summary(fit))
print(xt, type="html")
```